%%
% My resume, composed using LaTeX.
%
% @author: Carson DeSotel
% @created: 2020-05-20
% @updated: 2020-08-07
%%

\documentclass[10pt]{article}

\usepackage[T1]{fontenc}		% use for changing fonts
\usepackage[utf8]{inputenc}	% specify utf-8 encoding
\usepackage{utopia}			% font choice

\usepackage{enumitem}   		% for labels using enumeration

\usepackage[yyyymmdd]{datetime} % for date using ISO-8601
\renewcommand{\dateseparator}{--}

\usepackage{geometry}		% for margins
\geometry{
	letterpaper,				% page size
	headheight=20pt,
	headsep=10pt,
	margin=0.75in,
}

\usepackage{fancyhdr}		% remove footer page number
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{\hfill Last Updated: \today}
\renewcommand{\headrulewidth}{0pt}

\begin{document}
	\begin{center}
		{\LARGE \textbf{Carson DeSotel}} \\
		\vspace{5pt} 		% add a little more space for aesthetics
		(918) 809-2393 \ \textbf{|} \
		carson.desotel@gmail.com \ \textbf{|} \
		https://www.carsondesotel.com \
		
	\end{center}
		
	\section*{Education: \hrulefill} 
		\textbf{University of Minnesota - Twin Cities} \hfill 2018 - 2022 \\
		\indent BA, \textit{Computer Science} \hfill 2022 \\
		\indent \indent Courses focused on artificial intelligence, software design, and databases. \\
		\indent \indent
		\begin{tabular}{@{}l@{\ }l}
		\textbf{Capstone: } & Drone Image Recognition Simulation in C++ \\
		\end{tabular}
		\vspace{5pt}
		
		\indent BS, \textit{Geography} \hfill 2022 \\
		\indent \indent Courses focused on geographic information systems, urban geography, and geostatistics. \\		
		\indent \indent
		\begin{tabular}{@{}l@{\ }l}
		\textbf{Capstone: } & Image Segmentation for Tree Ring Slices in Python\\
		\end{tabular}
		
		\vspace{5pt}
		\indent 
		{Honors: }\\
		\indent \indent
		{Dean's List} \hfill Fall 2020, Spring 2021, Fall 2021, Spring 2022
			
	\section*{Experience: \hrulefill}
		\noindent
		\textbf{Optum} \hfill Remote \\
		\textit{Technology Development Program Associate} \hfill May 2022 - Present
		\begin{enumerate}[label=--]
			\item Deployed Kafka Connect microservices to stream over 2 million patient records across internal data platforms. 
			\item Worked on a fast-paced tiger team to create a critical data pipeline for patient and physician data. 
			\item Deployed software to Azure using Docker, Jenkins, and Kubernetes.
		\end{enumerate}
		
		\noindent
		\textbf{University of Minnesota - Twin Cities} \hfill Minneapolis, Minnesota \\
		\textit{Teaching Assistant} \hfill January 2019 - May 2022 
		\begin{enumerate}[label=--]
			\item Taught entry-level C++ programming and algorithms and data structures in Python and Java.
			\item Taught in lab settings for 7 semesters, both in-person and virtual.
		\end{enumerate}
		
		\noindent
		\textbf{Optum} \hfill Remote \\
		\textit{Technology Development Program Intern} \hfill June 2021 - August 2021
		\begin{enumerate}[label=--]
			\item Independently developed a Java application to test a model made using the Soar cognitive architecture to ensure its safety, efficiency, and reliability in a clinical setting.
			\item Detected and helped solve bugs in the cognitive architecture that could have misdiagnosed patients.
			\item Deployed software using Docker, GitHub, and Maven.
		\end{enumerate}		
		
		\noindent
		\textbf{Optum} \hfill Remote \\
		\textit{Technology Development Program Intern} \hfill June 2020 - August 2020
		\begin{enumerate}[label=--]
			\item Extended an open source governance platform while working as a full stack developer on an agile team.
			\item Selected to deliver a presentation and tech demonstration to executive at Optum and Optum - Ireland \\ alongside the entire Summer 2020 intern team across UnitedHealth Group and Optum.
		\end{enumerate}
		
	\section*{Technical Skills: \hrulefill}
		\begin{tabular}{@{}l@{\ }l}
		\textbf{Software: } & ArcGIS, Angular, Azure, CSS, Docker, Git, GNU/Linux (Ubunut, Arch), HTML, Jenkins, Kafka, \\ & Kubernetes, \LaTeX, Maven, Pandas
		\end{tabular}
		
		\vspace{5pt}
		\noindent
		\begin{tabular}{@{}l@{\ }l}
		\textbf{Programming Languages: } & C, C++, Java, JavaScript, Python, shell script, TypeScript\\
		\end{tabular}
		
		\vspace{5pt}
		\noindent
		\begin{tabular}{@{}l@{\ }l}
		\textbf{Languages: } & English (native), French (working proficiency) \\
		\end{tabular}
		
		\vspace{5pt}
		\noindent
		\begin{tabular}{@{}l@{\ }l}
		\textbf{Other: } &  agile development, cartography, database design, microservices, public speaking, web mapping \\
		\end{tabular}
			
%	\section*{Open Source Projects: \hrulefill}
%		\textbf{Personal Website} \hfill January 2019 - present \\
%		\textbf{Statistics Dashboard for Optum} \hfill June 2020 - August 2020 \\
%		\textbf{Personal Arch Linux System (Dotfiles)} \hfill August 2020 - present \\
%		\textbf{C++ Program to Display Pixel Art in Terminal} \hfill September 2020 \\
\end{document}